---
title: "Assignment_2"
author: "Group 7"
date: "4/14/2020"
output: html_document
---
Problem Statement :

To build a random forest classification model to predict the type of a breast tumor (benign or malignant). 
The data can be loaded using the mlbench library using- 
 library(mlbench)
 data(BreastCancer) 
A data frame with 699 observations on 11 variables, one being a character variable, 9 being ordered or nominal, and 1 target class.

a)	 Try examine the following values for the mtry variable 2 6 8.

b)	Show the confusion matrix of predictions on the test data (in the above example, I have the raw (class) predictions. You need to compare them with the ground truth values (i.e. testing$Class). Hint: table( ) function.


Solution :

Loading libraries and Data & checking the levels of the prediction :

```{r}

library(mlbench)
library(caret)
library(randomForest)
data(BreastCancer) 

levels(BreastCancer$Class)

```

Converting the character to numeric for ID and factoring Class. Removing NA's from the data : 

```{r}

BreastCancer$Id <- as.numeric(BreastCancer$Id) 
BreastCancer$Class <- as.factor(BreastCancer$Class)

BreastCancer <- na.roughfix(BreastCancer)

```

Dividing the data as training and testing :

```{r}

set.seed(2)
intrain <- createDataPartition(y = BreastCancer$Class, p = 0.7, list = FALSE)
training <-BreastCancer[intrain,]
testing <- BreastCancer[-intrain,]

```

Using Rain Forest method to train the model :

```{r}

rf.model<-train(Class~.,data=training,method='rf')
rf.model

```

Grid searching the training model with mtry variables- 2,6,8 :

```{r}

Grid_Serach <- expand.grid(.mtry=c(2,6,8))

rf.model2<-train(Class~., data=training, method='rf', tuneGrid=Grid_Serach)
rf.model2

```

The confusion matrix of predictions on the test data. And comparing the predictions with the ground truth values :

```{r}

probs <-predict(rf.model2,testing,type="prob")
head(probs)

pred_class <-predict(rf.model2,testing,type="raw")
head(pred_class)

table(pred_class, testing$Class)

```