---
title: "Assignment_4"
author: "Group 7"
date: "4/14/2020"
output: html_document
---

Problem Statement :

Building a Support Vector Machine models. The objective of the support vector machine algorithm is to find a hyperplane in an N-dimensional space that distinctly classifies the data points.

To build a SVM model to predict the type of a breast tumor (benign or malignant). 
The data can be loaded using the mlbench library using-
library(mlbench)
data(BreastCancer) 
A data frame with 699 observations on 11 variables, one being a character variable, 9 being ordered or nominal, and 1 target class.

a)	 Try examine the following values for the C parameter 1,2.5, 6.25.

b)	Show the confusion matrix of predictions on the test data. 


Solution :

Loading libraries and Data & checking the levels of the prediction :

```{r}

library(mlbench)
library(caret)
library(kernlab)
data(BreastCancer) 

levels(BreastCancer$Class)

```

Converting the character to numeric for ID and factoring Class. Removing NA's from the data : 

```{r}

BreastCancer$Id <- as.numeric(BreastCancer$Id)
BreastCancer$Class <- as.factor(BreastCancer$Class)

BreastCancer <- BreastCancer[complete.cases(BreastCancer),]

```

Dividing the data as training and testing :

```{r}
set.seed(2)
intrain <- createDataPartition(y = BreastCancer$Class, p = 0.7, list = FALSE)
training <-BreastCancer[intrain,]

testing <- BreastCancer[-intrain,]

```

Using SVM method to train the model :

```{r}

svm.model<-train(Class~.,data=training,method='svmLinear')
svm.model

```

Grid searching the training model with mtry variables- 1,2.5,6.25 :

```{r}

Grid_Serach <- expand.grid(.C=c(1,2.5,6.25))

svm.model2<-train(Class~., data=training, method='svmLinear', tuneGrid=Grid_Serach)
svm.model2

```

The confusion matrix of predictions on the test data. And comparing the predictions with the ground truth values :

```{r}

pred_class <-predict(svm.model2,testing,type="raw")
head(pred_class)

table(pred_class, testing$Class)

```